Timely Object Recognition

### 2012-05-28 writeups/nips12/evaluation.tex

\begin{figure}[h!]
\centering
\subfloat[Detection]{\includegraphics[width=0.78\linewidth]
    {figures/manual_plots_det_avg.png}} \\
\subfloat[Classification]{\includegraphics[width=0.78\linewidth]
    {figures/manual_plots_cls_whole.png}}
  \caption{Heuristic value function.}
  \label{fig:results_manual}
\end{figure}

@@

To summarize, we evaluate our system in the multi-class, multi-label detection and classification regime.
We evaluate on the PASCAL VOC 2007 dataset: training on the training and validation data and testing on the test set.
We run our policies on all images in the test set, cutting off execution at $T_d$.

@@

@@

\begin{figure}[h!]
\centering
\subfloat[Detection]{\includegraphics[width=0.78\linewidth]
    {figures/entropy_plots_det_avg.png}} \\
\subfloat[Classification]{\includegraphics[width=0.78\linewidth]
    {figures/entropy_plots_cls_whole.png}}
  \caption{Entropy reward function.}
  \label{fig:results_entropy}
\end{figure}

>>>>

@@

\begin{figure}[h!]
\centering
\subfloat[Occurence of a class with another]{\includegraphics[]
    {../figures/full_pascal_trainval_stats/cooccur_trim.png}} \hfill
\subfloat[Occurence of a class with two others]{\includegraphics[]
    {../figures/full_pascal_trainval_stats/cooccur_second_order_trim.png}}
  \caption{
  Co-occurrence statistics on the training portion of the PASCAL VOC 2007 dataset.
  In the first plot, a (row,column) cell shows the probability that an image that contains an object of the row class also contains an object of the column class.
  Accordingly, in the second plot, the probability that an image containing objects of the two classes listed in the row also contains an object of the column class.
  }
  \label{fig:dataset_stats}
\end{figure}

To summarize \autoref{sec:}, we evaluate our system in the multi-class, multi-label detection regime.
We evaluate on a popular detection challenge task: the PASCAL VOC dataset \cite{pascal-voc-2010}.
As shown in \autoref{fig:dataset_stats}, the dataset exhibits a rather modest amount of class co-occurrence, which puts our model in a disadvantaged setting.
$60\%$ of the images in the training set have only one class; $30\%$ have two classes, $7\%$ have three classes, and almost none have more.

Using the 2007 version of the dataset, we train on the training and validation data and test on the test set.
We run our policies on all images in the test set, cutting off execution at $T_d$.

@@

\begin{figure}[h!]
\centering
\subfloat[Detection]{\includegraphics[width=0.78\linewidth]
    {../figures/manual_plots_det_avg.png}} \\
\subfloat[Classification]{\includegraphics[width=0.78\linewidth]
    {../figures/manual_plots_cls_whole.png}}
  \caption{Heuristic value function.}
  \label{fig:results_manual}
\end{figure}

@@

\begin{figure}[h!]
\centering
\subfloat[Detection]{\includegraphics[width=0.78\linewidth]
    {../figures/entropy_plots_det_avg.png}} \\
\subfloat[Classification]{\includegraphics[width=0.78\linewidth]
    {../figures/entropy_plots_cls_whole.png}}
  \caption{Entropy reward function.}
  \label{fig:results_entropy}
\end{figure}
